---
title: "Karate Club Schism"
author: "Johannes Nakayama"
date: "1 4 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(igraph)
library(ggplot2)
library(tidyr)
library(forcats)
library(Matrix)
library(reshape2)
karate_outcomes <- readr::read_delim(file.path("data", "karate_outcomes.csv"), delim = ";")
SAVE <- FALSE
```



# Axelrod Model with Adjusted Initial Conditions

```{r}
outcomes_full <- arrow::read_feather(file.path("data", "simulation_outcomes", "outcomes_full.arrow"))
```

```{r}

outcomes_full %>% 
  mutate(id = as.character(id),
         config = factor(config)) %>% 
  group_by(id) %>% 
  mutate(mean_tendency = mean(tendency),
         median_tendency = median(tendency)) %>% 
  ungroup() %>% 
  arrange(desc(mean_tendency)) %>% 
  ggplot(aes(x = fct_inorder(id), y = tendency, color = config)) +
  geom_hline(yintercept = 0, alpha = 0.5, linetype = "dashed") +
  geom_point(alpha = 0.3) +
  geom_path(aes(group = config), alpha = 0.2) +
  scale_color_viridis_d() +
  labs(title = "Aggregate outcomes for different number of cultural dimensions", 
       x = "Agent ID", y = "Outcome tendency") +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "None")

if (SAVE) {
  ggsave(file.path("graphics", "classification_aggregate.pdf"), width = 7, height = 4.5)
}
```



CAVEAT: The order in which nodes are selected matters! The second node to be drawn has a much higher degree on average. This means that the interactions with our opinion leaders John A. and Mr. Hi are likely overrepresented. This is not necessarily a bad thing with regards to the interpretability of our model.



```{r}

mat <- readr::read_delim(file.path("data", "clustering_matrices", "config_003.txt"), delim = ",", col_names = FALSE)
mat <- Matrix::as.matrix(mat)
longdata <- melt(mat)

longdata %>% 
  ggplot(aes(x = Var2, y = Var1)) +
  geom_raster(aes(fill = value)) +
  scale_fill_viridis_c() +
  coord_fixed()

```












# Axelrod Model with Random Configuration

```{r}

random_cfg <- arrow::read_feather(file.path("data", "simulation_records", "random_config.arrow"))

```



```{r}

random_cfg %>% 
  filter(step == max(step)) %>% 
  select(replicate, culture) %>% 
  distinct() %>% 
  group_by(replicate) %>% 
  summarize(unique_cultures = n()) %>% 
  ungroup() %>% 
  group_by(unique_cultures) %>% 
  summarize(count = n()) %>% 
  ungroup()

```


```{r}
random_cfg %>% 
  filter()
```




# Classical Model of Opinion Dynamics

```{r}

classical_model <- arrow::read_feather(file.path("data", "classical_model", "classical_model.arrow"))

```


```{r}

# example replicate
classical_model %>% 
  filter(replicate == 6) %>% 
  ggplot(aes(x = step, y = opinion, color = factor(id))) +
  geom_line() +
  ylim(c(-1, 1)) +
  theme_bw() +
  theme(legend.position = "None")

# consensus in all runs
classical_model %>% 
  filter(step == max(step)) %>% 
  select(-step) %>% 
  group_by(replicate) %>% 
  summarize(mean_opinion = mean(opinion),
            var_opinion = round(var(opinion), 3)) %>%
  ungroup() -> tmp 

max(tmp$var_opinion)

tmp %>% 
  ggplot(aes(x = replicate, y = mean_opinion)) +
  geom_point() +
  ylim(c(-1, 1)) +
  theme_bw()


```



# Friedkin-Johnson Model

```{r}

friedkin_johnson <- arrow::read_feather(file.path("data", "friedkin_johnson", "friedkin_johnson.arrow"))
# rm(friedkin_johnson)
```


```{r}

friedkin_johnson %>% 
  # filter(replicate == 3) %>% 
  filter(step <= 15) %>% 
  ggplot(aes(x = step, y = opinion, color = factor(id), group = interaction(id, replicate))) +
  geom_line(size = 0.6, alpha = 0.3) +
  # geom_jitter() +
  theme_bw() +
  theme(legend.position = "None")

```


# Hegselmann-Krause Model


```{r}
hegselmann_krause <- arrow::read_feather(file.path("data", "hegselmann_krause", "hegselmann_krause.arrow"))
```


```{r}
hegselmann_krause %>% 
  filter(epsilon == 0.5, replicate == 1) %>% 
  filter(step <= 10, id == 1) %>% 
  ggplot(aes(x = step, y = opinion, color = factor(id))) +
  geom_line() +
  theme(legend.position = "None")
```



```{r}

hegselmann_krause %>% 
  filter(replicate == 3) %>% 
  filter(step <= 100) %>% 
  ggplot(aes(x = step, y = opinion, color = factor(id))) +
  geom_line() +
  theme(legend.position = "None") +
  facet_wrap(. ~ factor(epsilon))

```


```{r}

hegselmann_krause %>% 
  filter(epsilon == 0.5, replicate <= 20) %>% 
  filter(step <= 100) %>% 
  ggplot(aes(x = step, y = opinion, color = factor(id))) +
  geom_line() +
  theme(legend.position = "None") +
  facet_wrap(. ~ factor(replicate))

```


```{r}

hegselmann_krause %>% 
  filter(step == 50) %>% 
  filter(epsilon == 0.5) %>% 
  group_by(id) %>% 
  mutate(mean_tendency = mean(opinion)) %>% 
  ungroup() %>% 
  arrange(desc(mean_tendency)) %>% 
  ggplot(aes(x = fct_inorder(factor(id)), y = opinion, color = factor(replicate))) +
  geom_jitter(alpha = 0.1) +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "None")
  

```




































